---
title: "Portable Routines for Preparing CCES and ACS data for MRP"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Cite as:

* Shiro Kuriwaki (2020). ccesMRPprep: Functions to Prepare CCES data for MRP. R package. <https://www.github.com/kuriwaki/ccesMRPprep>


### Purpose and Contribution

Multi-level Regression and Post-stratification is an increasingly popular method for analyzing surveys, and can be implemented on public datasets such as the [CCES](https://cces.gov.harvard.edu/) and ACS. However, there are considerable upfront costs in preparing the data, recoding values and generating post-stratification frames so data can be matched.

This package provides data loading, processing, and formatting functions for a particular task: using _CCES data_ for MRP. Its key contributions are functions that are calibrated to a consistent syntax, lookup tables and value-key pairs of data that are based upon a careful reading of data sources, and data loading functions that use APIs to reduce the dependency on downloading large files. Model fitting and visualization of MRP itself is handled elsewhere. This package is focused on the preparation to get there. 
   
   
```{r, echo = TRUE, message = FALSE}
# remotes::install_github("kuriwaki/ccesMRPprep")
library(ccesMRPprep)
library(tidyverse)
```

See the vignettes for more long-form workflow overviews (`vignette("overview")`) and documentation and explanation of the nature of the data (`vignette("acs")`).  Otherwise, each function and built-in data provides documentation as well. 


## Workflow

See the overview vignette (`vignette("overview")`) from a illustrative workflow.


## Related Packages

- <https://github.com/kuriwaki/rcces> has another set of CCES related functions, but these
are either my own personal functions in development (not for production), or specific to 
non-MRP projects.
- <https://github.com/kuriwaki/CCES_district-opinion> is a private package that uses (among others) this package to process large CCES data for MRP at scale. 


## Support

This package is a part of the CCES MRP project, supported by NSF Grant 1926424: [Bayesian analytical tools to improve survey estimates for subpopulations and small areas](https://nsf.gov/awardsearch/showAward?AWD_ID=1926424). The contents are based on collaborations and helpful discussions with Ben Bales, Lauren Kennedy, Mitzi Morris, and Soichiro Yamauchi.
