---
title: "CPS Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CPS Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, include = FALSE}
library(ccesMRPprep)
library(tidyverse)
library(haven)
library(knitr)
options(knitr.kable.NA = '')

xt <- function(var, tbl = cps_onewaytabs) {
  tbl %>% 
    filter(variable == quo_name(enquo(var)), year >= 2006) %>% 
    pivot_wider(id_cols = name, names_from = year, values_from = n) %>% 
    rename({{var}} := name) %>% 
    knitr::kable(format.args = list(big.mark = ','), )
}
```



The CPS is a survey that includes self-reported vote, as well as a variety of other economic indicators. It has less geographic granularity than the ACS.


The CPS runs monthly, and in a given month collects about 130,000 repondents, or the twice the amount the CCES collects in a year. Only the November survey includes a "Voter Supplement", which includes a question about the respondent's vote turnout.

# Variable and counts

We list the counts of key demographic variables here, using the one-way tabulations in `?cps_onewaytabs`

## sex

```{r, echo = FALSE}
xt(sex)
```
## age (5-way)


```{r, echo = FALSE}
xt(age)
```


## education

```{r, echo = FALSE}
xt(educ)
```

## race

```{r, echo = FALSE}
xt(race)
```

## hispanic origin

```{r, echo = FALSE}
xt(hispan)
```


## Self-reported vote

```{r, echo = FALSE}
xt(voted)
```

## state

```{r, echo = FALSE}
xt(statefip)
```


## county (if not anonymized)

```{r, echo = FALSE}
xt(county)
```
