---
title: "Workflow Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(ccesMRPprep)
library(tidyverse)
```

## **Step 1.** Loading CCES data

All CCES data can be downloaded directly from dataverse, using the development version of the `dataverse` R package.  Once you set your dataverse API token, the function `get_cces_dv` will make this quick and simple. 


```{r, eval = FALSE}
ccc <- get_cces_dv("cumulative")
```

We will use a built-in sample of 1,000 observations for illustration (see `?ccc_samp`).

```{r}
ccc_samp
```



##  **Step 2.** Cleaning CCES data

The CCES cumulative dataset is already harmonized and cleaned, but values must be recoded so that they later match with the values of th ACS. I have created key-value pairings for the main demographic variables. The wrapper function expects a CCES cumulative dataset and recodes.

See `?get_cces_question` for how to get the _outcome_ data, which is a single column from another CCES dataset. This still relies on a flat file being pre-downloaded (via `?get_cces_dv`. 

```{r}
ccc_std <- ccc_std_demographics(ccc_samp)
```



##  **Step 3.** Preparing the brms function

We presume the formula will be used in brms. Currently we support binary outcomes. This can be modeled as a binomial, which in brms is of the form

```{r}
fm_brm <- yes | trials(n_responses) ~  age + gender + educ + pct_trump + (1|cd)
```


A prior could be specified here as well, but this is not strictly necessary and can be defined when fitting the model. 


##  **Step 4.** Collapsing the CCES data

For speed, we collapse the individual-level data where each outcome is binary to a count dataset where each row is a cell (with a trial and success value). This form also makes drawing posteriors much easier in the next step. We use `?build_counts` for this, which takes a individual-level dataset (built from `?ccc_std_demographics`, or further passed through `?ccces_join_slim` for all relevant outcomes and predictors).

```{r}
# fake outcome data - must be called "response"
set.seed(02138)
ccc_samp_std <- ccc_samp %>% 
   mutate(response = sample(c("For", "Against"), size = n(), replace = TRUE)) %>% 
   ccc_std_demographics()

ccc_samp_out <- build_counts(ccc_samp_std,
                             "yes | trials(n_response) ~ age + gender + educ")

ccc_samp_out
```


##  **Step 5.** Prepare a post-stratification table, after preparing ACS data

We provide wrappers around the great [tidycensus](https://walker-data.com/tidycensus/) package
that produces ACS data and post-stratification tables from the ACS. A considerable amount of
lookup tables internally will pull out the apporpriate CD-level counts and label them
so that they match up with CCES keys. District-level information, which is not necessary ACS data (e.g. election outcomes) must be supplied here as well/

```{r, eval = FALSE}

 acs_tab <- get_acs_cces(
              varlist = acscodes_age_sex_educ,
              varlab_df = acscodes_df,
             .year = 2018)

 poststrat <-  get_poststrat(acs_tab, cd_info_2018, fm_brm)
```

##  **Final Output**

Under this workflow, only three objects are needed to conduct MRP with a brms model:

- The model specification which can be a plain text line of a brms formula (in Step 3)
- The survey data that is formatted via `?build_counts` at the end (in Step 4)
- The poststratification table via `?get_poststrat` (in Step 5).

Together, these uniquely define one MRP model for one operationalization of one question with a particular set of covariates. 

