---
title: "Synthetic Target Estimation"
output: 
  rmarkdown::html_vignette:
    fig_width: 8
    fig_height: 4
vignette: >
  %\VignetteIndexEntry{Synthetic Target Estimation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(ccesMRPprep)
library(tidyverse)

library(scales)
library(furrr)
plan(multisession, workers = 6)
```

Almost all survey weighting, whether MRP or not, face a data limitation that direct knowledge of the joint distributions of predictors (such as race, partisanship, and geography) are limited. There is a long tradition of statistical and applied work that seeks to expand the set of available interactions to poststratify on. These techniques can roughly be called synthetic population imputation. Again, there is a long tradition of this; iterative proportional fitting (Deming and Stephan), ecological inference, and latent factorization methods can be thought of as being related.

We can classify the main approaches by what outside data they leverage:

| Main Idea              | Functions | Examples |
|------------------------|-----------|----------|
| Use Population Margins | `synth_prod()` | Leemann and Wasserfallen (2017) |
| Use Microdata          | `synth_mlogit()` | Kastellec et al. (2015)|
| Combine both           | `synth_smoothfix()` | Ghitza and Steiz (2020)|
|                        | `synth_bmlogit()` |  Yamauchi (2021) |


## Validation of Multiple Methods

We provide a simple set of functions to implement this. We extend the ACS table assisted by a survey model using a function called `synth_mlogit()`.

```{r}
acs_syn_mlogit <- synth_mlogit(race ~ female + age,
                               microdata = cc18_NY,
                               poptable = acs_race_NY,  
                               area_var = "cd")
```

The ccesMRPprep package provide two other approaches to estimating the joint -- these incorporate another source of information, which is the margins that are available.

```{r}
race_margins <- collapse_table(acs_race_NY, area_var = "cd", X_vars = "race", 
                               count_var = "count", new_name = "count")
race_margins
```

Given this data that is simply the marginal distribution of race in each CD, one option is to simply take the product assuming independence

```{r,warning=FALSE}
acs_syn_prod <- synth_prod(race ~ female + age,
                           poptable = acs_race_NY,
                           newtable = race_margins,
                           area_var = "cd")
```

A more sophisticated method is to combine these two sources of information: microdata and known outcome margins. Ghitza and Steitz did a two-step process, where they first did survey modeling to smooth cells and then fixed *those* margins to the known population margins.

```{r}
acs_syn_fix1 <- synth_smoothfix(race ~ female + age, 
                               microdata = cc18_NY,
                               poptable = acs_race_NY, 
                               fix_to = race_margins,
                               area_var = "cd")
```

Yamauchi developed a multinomial logit that simultaneously imposes the same sort of balancing constraint. The benefit of this method is that the rake weighting does not nullify the survey data, and the tolerance range can be controlled.

```{r, warning=FALSE}
acs_syn_fix2 <- synth_bmlogit(race ~ female + age, 
                               microdata = cc18_NY,
                               poptable = acs_race_NY, 
                               fix_to = race_margins,
                               area_var = "cd")
```

The benefit of this example is that we can examine how our estimated counts of this synthetic table compared with the actual values of the joint distribution. Here is a scatter plot comparing the counts. Each point represents a cell: [14 congressional districts] x [2 gender categories] x [5 age categories] x [6 race categories].

```{r, echo = FALSE, message=FALSE,warning=FALSE, fig.height=3.5, fig.width=7}

syn_val <- select(acs_syn_prod, cd, female, age, race, count_rake = count) %>% 
  left_join(rename(acs_syn_mlogit, count_smooth = count),
            by = c("cd", "female", "age", "race")) %>%
  left_join(rename(acs_syn_fix1, count_smoothfix = count),
            by = c("cd", "female", "age", "race")) %>%
  left_join(rename(acs_syn_fix2, count_bmlogit = count),
            by = c("cd", "female", "age", "race")) %>%
  left_join(count(acs_race_NY, cd, female, race, age, wt = count, name = "count_truth"),
            by = c("cd", "female", "age", "race")) %>% 
  select(cd, female, age, race, matches("count_"))

syn_val_long <- syn_val %>% 
  pivot_longer(c(count_rake, count_smooth, count_smoothfix, count_bmlogit), 
               names_to = "method",
               values_to = "estimate",
               names_prefix = "count_") %>% 
  mutate(method = recode_factor(
    method, 
    smooth = "Survey Model\n(synth_mlogit)", 
    rake = "Simple Product\n(synth_prod)",
    smoothfix = "Survey + Fix to Outcome\n(synth_smoothfix)",
    bmlogit = "Simultaneous Constraint\n(synth_bmlogit)"))

syn_val_long %>% 
  ggplot(aes(count_truth, estimate, color = race)) +
  facet_wrap(~ method, nrow = 1) +
  geom_abline(linetype = "dashed") +
  geom_point(size = 0.5, alpha = 0.5) +
  theme_bw() +
  coord_equal() +
  scale_x_continuous(labels = comma) +
  scale_y_continuous(labels = comma) +
  labs(x = "True Joint Table Count",
       y = "Estimate",
       color = "Race/Ethnicity of Cell") +
    theme(legend.position = "bottom", 
        panel.grid = element_blank())
```

The first plot does not look great. The simple product does surprisingly well. It is after all perhaps not surprising that it is hard to estimate education from age bins and gender. The main difference seems to be that in all the other three cases, we are fixing outcomes to _CD-level_ education margins. _`bmlogit`_ would do worse, for example, if we only fixed to the _State-level_ margins.




## Real Applications

We have a age x gender x education table and a age x gender x race table, but not a four-way table. Here, we use the synthetic estimators to estimate this joint table.

We know the margins of education in each congressional district in NY:


```{r}
educ_target <- count(acs_educ_NY, cd, educ, wt = count, name = "count")
educ_target
```

Unfortunately, these will be collapsed statewide for now.

For bmlogit and mlogit

```{r, warning=FALSE, message=FALSE}
# No constraint
pop_svy <- synth_mlogit(educ ~ race + age + female,
                        microdata = cc18_NY,
                        poptable = acs_race_NY,
                        area_var = "cd")

# With constraint
pop_bm <- synth_bmlogit(educ ~ race + age + female,
                        microdata = cc18_NY,
                        fix_to = educ_target,
                        poptable = acs_race_NY,
                        area_var = "cd")
```
Here we show the main estimates of the model, which are conditional probability given X strata. We fix to women and a CD, `NY-01` which is the tip of Long Island, New York (Lee Zeldin, R; 70% White).  The CD does not matter as long as the targets are at the state level the CDs do not matter.


```{r, echo=FALSE, fig.height=5, fig.width=6.2}
plot_tiles <- function(tbl, tit, show_cd = "NY-01") {
  tbl %>% 
  filter(cd == show_cd, female == 1) %>% 
  mutate(educ = fct_inorder(educ), 
         pct_fmt = percent(prZ_givenX, accuracy = 1),
         age = fct_rev(age)) %>%  
  ggplot(aes(y = age, x = educ, fill = prZ_givenX)) +
  facet_wrap(~ race) + 
  geom_tile(color = "white", size = 1) + 
  scale_fill_viridis_b(end = 0.8) +
  guides(fill = guide_bins(title.position = "top", keywidth = unit(2, "cm"))) +
  geom_text(aes(label = pct_fmt), color = "white", size = 2) + 
  theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.text = element_text(color = "black"),
        axis.text.x = element_text(angle = 90)) + 
  labs(fill = "Pr(Education | Age, Race)",
       title = tit,
       y = NULL, x = NULL)
}

plot_tiles(pop_svy, "CCES Estimates (synth_mlogit), NY-01")
```


```{r, echo=FALSE, fig.height=5, fig.width=6.2}
plot_tiles(pop_bm, "CCES fixed to CD Education Margins, NY-01\n(synth_bmlogit)")
```

Recall that bmlogit balances to the _area_ level population targets if available, whereas there is no balancing in the mlogit, and both always use the entire microdata without subsetting to area.  So, the values should be somewhat different if subsetting to a different CD, like NY-14  (D, Ocasio-Cortez) where 49% of the population is Hispanic.

```{r, echo=FALSE, fig.height=5, fig.width=6.2}
plot_tiles(pop_bm, show_cd = "NY-14", "CCES fixed to CD Education Margins, NY-14\n(synth_bmlogit)")
```


Whereas the values would be the same regardless of district in the mlogit implemenation.

```{r, echo=FALSE, fig.height=5, fig.width=6.2}
plot_tiles(pop_svy, show_cd = "NY-14", "CCES Estimates (synth_mlogit), NY-14")
```
